SPARQL on the Open, Decentralised Web

### 2016-07-30 dissertation/acknowledgments.tex
and Helen

Finally, my industry colleagues David Norheim and Robert Engels have
also been important in shaping my technical understanding and my
ideas.

>>>>

My industry colleagues David Norheim and Robert Engels have
also been important in shaping my technical understanding and my
ideas.

Finally, many thanks to Helen Murray for linguistic assistance.
